\subsection{Determination of $\hat{m}_{\Pgt\Pgt}$}
\label{sec:mem_numericalMaximization}

The best estimate, $m_{\Pgt\Pgt}$, for the mass of the $\Pgt$ lepton pair in a given event
is obtained by computing the probability density $\mathcal{P}(\bm{p}^{\vis(1)},\bm{p}^{\vis(2)};\pX^{\rec},\pY^{\rec}|m_{\PHiggs}^{\textrm{test}(i)})$ 
for a series of mass hypotheses $m_{\PHiggs}^{\textrm{test}(i)}$, using Eq.~(\ref{eq:mem_with_hadRecoil}), and determining the value of $m_{\PHiggs}$ that maximizes this probability density.
The integral in Eq.~(\ref{eq:mem_with_hadRecoil}) is evaluated numerically using the VAMP algorithm.
For each mass hypotheses $m_{\PHiggs}^{\textrm{test}(i)}$ the integrand is evaluated $20,000$ times.
The series of mass hypotheses is defined by a recursive relation: 
\begin{equation}
m_{\PHiggs}^{\textrm{test}(i + 1)} = (1 + \delta) \,  m_{\PHiggs}^{\textrm{test}(i)} \, \mbox{ with } \, m_{\PHiggs}^{\textrm{test}(0)} = m_{\vis} \, ,
\label{eq:mTauTau_step_size}
\end{equation}
where $m_{\vis}$ denotes the mass of the visible $\Pgt$ decay products.
The step size $\delta$ is chosen such that it is small compared to the
expected resolution on $m_{\PHiggs}$,
typically amounting to $15$--$20\%$ relative to the true mass of the $\Pgt$ lepton pair.
In order to reduce the computing time, the series is computed in two passes.
The purpose of the first pass, which uses a step size $\delta = 0.10$, is to find an approximate value of $m_{\Pgt\Pgt}$
that maximizes the probability density $\mathcal{P}(\bm{p}^{\vis(1)},\bm{p}^{\vis(2)};\pX^{\rec},\pY^{\rec}|m_{\PHiggs}^{\textrm{test}(i)})$.
The series of mass hypotheses that is used in the first pass stops when $\mathcal{P}(\bm{p}^{\vis(1)},\bm{p}^{\vis(2)};\pX^{\rec},\pY^{\rec}|m_{\PHiggs}^{\textrm{test}(i)})$ falls below one per mille 
of the maximal probability density $\mathcal{P}^{\textrm{max}}$
computed for any $m_{\PHiggs}^{\textrm{test}(i)}$ so far in a given event.
In the second pass, which uses a step size of $\delta = 0.01$,
further $\mathcal{P}(\bm{p}^{\vis(1)},\bm{p}^{\vis(2)};\pX^{\rec},\pY^{\rec}|m_{\PHiggs}^{\textrm{test}(i)})$ values 
are computed for mass hypotheses $m_{\PHiggs}^{\textrm{test}(i)}$ that
are within a region around the maximum
for which the probability density computed in the first pass exceeds
$0.10 \cdot \mathcal{P}^{\textrm{max}}$.
Finally, the graph of $\log \left( \mathcal{P}(\bm{p}^{\vis(1)},\bm{p}^{\vis(2)};\pX^{\rec},\pY^{\rec}|m_{\PHiggs}^{\textrm{test}(i)}) \, \cdot \, \mbox{\GeV}^{8} \right)$ 
versus $m_{\PHiggs}^{\textrm{test}(i)}$ is fitted by a second order polynomial
in the region around the maximum,
and $m_{\Pgt\Pgt}$ is taken to be the point at which the polynomial reaches its maximum.
